### 2015-03-23 paper.tex
Added copyleft and GPLv2

\documentclass[12pt,letterpaper]{article}
\usepackage{ifpdf}
\usepackage{listings}
\usepackage[parfill]{parskip}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{wrapfig}
\renewcommand{\abstractname}{Executive Summary}
\titlespacing*{\section}{0pt}{12pt plus 4pt minus 2pt}{0pt plus 4pt minus 2pt}
\titlespacing*{\subsection}{0pt}{12pt plus 4pt minus 2pt}{0pt plus 4pt minus 2pt}
\begin{document}

@@

@@

\newpage
\section*{References}

\begin{itemize}[label={},itemindent=-15pt]

\item \openup 0.5em References go here.

\end{itemize}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{ifpdf}
\usepackage{listings}
\usepackage[parfill]{parskip}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{url}
\renewcommand{\abstractname}{Executive Summary}
\titlespacing*{\section}{0pt}{12pt plus 4pt minus 2pt}{0pt plus 4pt minus 2pt}
\titlespacing*{\subsection}{0pt}{12pt plus 4pt minus 2pt}{0pt plus 4pt minus 2pt}
\begin{document}

@@

Copyleft licenses are used to keep software both free and open. As opposed to permissive licenses, copyleft license require that all derived works be distributed under the same terms of the original work. This ensures that all derived works maintain the same freedoms. However, as a result of this restriction, many copyleft licenses are often left incompatible with other licenses. \cite{copyleft}

\subsection{GNU GPLv2}

The GNU General Public License License v2 or GPLv2 is the most commonly used free software license today. It is used in project including; Linux, The GNU GPL, first developed in 1989 by Richard Stallman, was designed to allow for the distribution of the GNU project; ensuring that any derived copies would maintain the same freedoms associated with the project. In 1991 the GPLv1 license was revised to create the GPLv2 license. This revision however was only a rephrase of the original license and did not introduce any new legal implications.

Some of the main features of the GNU GPLv2 include: \cite{gpl2}

\begin{itemize}
\item The ability to copy and redistribute unmodified source code
\item The ability to modify and redistribute modified source code
\item The ability to distribute a compiled version of the software considering that all copies contain a copyright notice and exclusion of warranty.
\item All modified copies are distributed under the GPLv2 license
\item All compiled programs must be accompanied with the corresponding source code or be provided access to the source code.
\end{itemize}

@@

\newpage

\begin{thebibliography}{9}
\bibitem{copyleft} GNU Operating System. What is Copyleft? \url{https://www.gnu.org/copyleft/}.

\bibitem{gpl2} GNU Operating System. GNU General Public License, version 2. \url{https://www.gnu.org/licenses/gpl-2.0.html}.

\end{thebibliography}

% \section*{References}

% \begin{itemize}[label={},itemindent=-15pt]

% \item \openup 0.5em References go here.

% \end{itemize}
